Untrusted B2B Collaboration using the Blockchain

### 2018-07-18 paper/paper.tex
Work on solution approach

\section{Solution approach}

basic understanding/ intuition
-> make orchestration possible

use one contuous example

visualizations !!

\subsection{Contract Structure}

factory (maps to process)
creates instance (maps to process instance)
also access contract for user rights management

\subsection{Authorization}

access contract API

>>>>

\section{Solution approach}
We propose a system design, that allows choreographies to be executed publicly on the blockchain.
In order to achieve this, every organization to provides an interface for their public process using smart contracts.
We assume that all participating organizations use a process engine to execute their private processes.
When a throw event is triggered within a process engine, a \emph{throw event function} is called on a smart contract and the corresponding \emph{catch event function} is called on the smart contract of the organization responsible for catching the event.
Thus, the public processes of all organizations are recorded on the blockchain.

%TODO reference "trigger" from Untrusted paper
Each organization uses a \emph{trigger} that continuously listens to catch events.
If a catch event is observed, this information is relayed to the process engine to handle the event.
The usage of the blockchain to monitor the choreography is encapsulated in the process engine and is therefore hidden from the users.

%basic understanding/ intuition
%-> make orchestration possible

%use one contuous example

%visualizations !!

\subsection{Contract Structure}
To realize the system, we use three kinds of smart contracts.
Firstly, each organization uses one \emph{instance contract} per process instance.
It represents the public process of the organization for the corresponding process.
It is called during the process execution when a catch or throw event is reached in the process instance.
When this happens, it emits an event on the blockchain to document this fact.

Secondly, each organization uses one \emph{factory contract} per process.
It is responsible for creating instance contracts and saving a mapping from instance IDs to the corresponding contracts.

Thirdly, each organization uses \emph{access contracts} to manage which users can trigger events on the instance contracts.
Either, there is on access contract per process or access contracts are shared over multiple processes depending on the use case.

%factory (maps to process)
%creates instance (maps to process instance)
%also access contract for user rights management

\subsection{Authorization}
In order to authorize users, the instance contract calls the access contract.
